---
title: "S&DS 625 Introduction"
date: "August 30, 2017"
output: pdf_document
---

## Computing and Reproducible Research

This document was produced in RStudio using R Markdown, choosing
the PDF option for the document.  You can work without RStudio, but
RStudio makes many things like this wonderfully easy.
And R Markdown itself is pretty simple (far simpler
than full-blown \LaTeX).  You'll need packages `knitr` and
`rmarkdown`, which are bundled in with RStudio.  
You'll also want \LaTeX\ on your system,
though you won't use it directly.  In Windows, this is called
`MiKTeX`.  The **full, complete distribution** is required (and is
quite large, about 2 GB -- don't try to download it during class,
please).  The `MiKTeX` installer will really try to encourage you to
install the basic version.  It won't work. On the Mac, you'll need `MacTeX`.  
It's an easy installation.  

Recommendation: start by installing R (www.r-project.org) and
either `MiKTeX` or `MacTeX`.  Then install RStudio.  


## Some Advice

Work together on computing stuff like this!  There are lots of little
computing "gotchas" that can
be annoying, but fighting through them and succeeding is important.  When
you graduate and get a real job (or head to graduate school or whatever),
being able to solve problems and be computationally self-sufficient will
be valuable.  Yes, we're here to study statistics (or data analysis,
we would prefer to say).  

## Markdown?

Looking for information about Markdown? 
Try http://daringfireball.net/projects/markdown/ or a more concise "cheat sheet" at https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf.

## LaTeX?

Let's call this essential if you are doing a PhD -- you'll use it
for your dissertation and for 95\% of the papers you write.  But for
many it is probably overkill and R Markdown and R scripts will be
sufficient.  As a side note, you can include many \LaTeX\ things in
R Markdown documents.

## Toy Example

Let's try working with a dataset. This is
a code chunk, which is processed and nicely displayed with the output
in the resulting PDF:

```{r}
x <- read.csv("https://www.dropbox.com/s/3qlh23gz41vz908/Diving2000.csv?raw=1",
              as.is=TRUE)
dim(x)
mean(x$JScore)
```

And R Markdown also makes it easy to integrate graphics.  (Note that only
one graphical display should appear in any one code chunk.)

```{r}
hist(x$JScore, xlab="Score",
     main="Distribution of Judges' Scores",
     breaks=seq(-0.25, 10.25, by=0.5))
```



## Reproducible?

This document is entirely ___reproducible___ as long as you have the original
R Markdown file, `1-1_Intro.Rmd`. You should be able to reproduce this document
exactly (or with perhaps superficial formatting differences), including all 
the analysis and the plot.  Using
\LaTeX\ involves a similar workflow that includes code with the
document, but is (potentially) more complicated (and hence potentially
much more sophisticated). 


## In this course...

The choice of computing environment (plain vanilla R GUI vs. RStudio) is left up to you. I will be picky on coding style and efficiency. Bad code leads
to mistakes and wasted time. Communication is also important, as this is a course about data analysis... so effectively, neatly, and concisely
presenting your work will be an important component of the course.

## TODAY

- Syllabus
- Hoops data scrape example
- Basic New Haven real estate property record toy scrape and challenge
- Homework for Friday (because it is effectively a Monday)


## Homework Due Friday

I will provide a link to the VisionAppraisal files, zipped. Please download from this link and unpack the zip file. 
That is, please don't scrape the data directly
from the web site -- it generates lots of traffic (more than 1.5 GB per batch)
and may cause problems.

For Friday, write a script that will parse files associated with pid 1 through 1000 (when available) and creates a data frame with three columns (and 1000 rows):

* parcel id (call it `pid`),
* raw address (call it `location`)
* year built (call it `yearbuilt`)

You'll have a row for each property -- if there is
no information (or no raw file) there should still be a row for it in the
data set (with the `pid` but `NA` values for the other variables).
Example: for parcel number 600, the `pid` would be 600,
the `location` would be "108 HYDE ST", and the `yearbuilt` would be 1910.

Submit your script as "hw1.R" by Friday 11AM onto Canvas. Indentation and
quality of code matters.  The comments at the top of the script should acknowledge any
collaboration (working together is fine but your script should be your own
work and you should understand everything that you do). 


